Decentralized Data Marketplace to Enable Trusted Machine Economy $^{\dagger}$

### 2019-12-19 paper.tex
Modify session key exchange

Next, session key $k$ should be exchanged between the data provider and consumers. Instead of using off-chain solution which is efficient and low-cost, we use smart contract to transfer the session key\cite{3tierDataMarket} that is easy to trace the record and prevent malicious participants to cheat others.

>>>>

Next, session key $k$ should be exchanged between the data provider and consumers. To exchange data, some researchs\cite{Medrec} seek an off-chain solution which uses an end-to-end communication that is efficient and low-cost. However, it is hard to avoid that the data source is unavailable or the sender sends incorrect data intentionally. Instead of using off-chain solution, we use smart contract to transfer the session key\cite{3tierDataMarket} that not only ensures the consistency of the session key, the availability of the source and the traceability of the record, but also prevents malicious participants to cheat others.
